---
output: github_document
---

<!-- badges: start -->
[![minimal R version](https://img.shields.io/badge/R%3E%3D-`r getOption("ew.required.r")`-6666ff.svg)](https://cran.r-project.org/)
[![Netlify Status](https://api.netlify.com/api/v1/badges/bcc3fe43-1cd0-4d23-aca4-42f78a809855/deploy-status)](https://app.netlify.com/sites/happy-chandrasekhar-239442/deploys)
[![Build Status](https://img.shields.io/travis/timtrice/enhanced_workflowr/master.svg)](https://travis-ci.org/timtrice/enhanced_workflowr)
[![Docker Cloud Build Status](https://img.shields.io/docker/cloud/build/timtrice/enhanced_workflowr.svg?style=popout)](https://cloud.docker.com/repository/docker/timtrice/enhanced_workflowr)
[![Launch Rstudio Binder](http://mybinder.org/badge.svg)](https://mybinder.org/v2/gh/timtrice/enhanced_workflowr/master?urlpath=rstudio)
[![Launch rstudio.cloud](https://img.shields.io/badge/launch-rstudio.cloud-yellowgreen.svg)](https://rstudio.cloud/project/417421)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

# `r desc::desc_get_field("Package")` (`r desc::desc_get_version() `)

## `r desc::desc_get_field("Title") `

### Prerequisites

```{r packages, echo = FALSE}
knitr::kable(
  desc::desc_get_deps()[,2:3], 
  col.names = c("Package", "Version"), 
  caption = "Required R packages to run this project."
)
```

## Built With

* [R `r getOption("ew.required.r")`](https://www.r-project.org/) - The R Project for Statistical Computing

## Support

Please see [SUPPORT](`r desc::desc_get_urls()`/blob/master/.github/SUPPORT.md) if you should find any discrepancies in this project.

## Contributing

Please read [CONTRIBUTING.md](`r desc::desc_get_urls()`/blob/master/.github/CONTRIBUTING.md) for details on our code of conduct, and the process for submitting pull requests to us.

Please note that the '`r desc::desc_get_field("Package")`' project is released with a [Contributor Code of Conduct](`r desc::desc_get_urls()`/blob/master/.github/CODE_OF_CONDUCT.md). By contributing to this project, you agree to abide by its terms.

## Versioning

We use [SemVer](http://semver.org/) for versioning. For the versions available, see the [tags on this repository](`r desc::desc_get_urls()`/tags). 

## License

This project is licensed under the MIT License - see the [LICENSE](`r desc::desc_get_urls()`/blob/master/LICENSE.md) file for details

## Authors

```{r authors, echo = FALSE, results = "asis"}
authors <- desc::desc_get_authors()
for (author in authors) {
  if ("aut" %in% author$role) {
    cat(sprintf(
      fmt = "* [%s, %s](%s)", 
      author$family, 
      author$given, 
      getOption("ew.user_info")[[author$email]]$git_user_profile)
    )
  }
}
```

## Acknowledgements

See the list of [contributors](`r desc::desc_get_urls()`/contributors) who participated in this project.
